NFC and burnout in teachers - A replication and extension study

### 2022-07-26 Manuscript/Revision_Letter.Rmd
finished answers

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
We would like to thank the reviewers for their efforts to thoroughly assess our manuscript. In the following we address your and each reviewer's concerns point-by-point.
We hope that we could adequately address all the issues raised.

@@

@@

This is our response.

@@

@@

Thank you for this suggestion.
The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
Each part is relevant but not "long enough" to warrant its own paper.

\Assignment{JZ \& AS \& AS}
\WorkInProgress

>>>>

thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_.
We would like to thank the reviewers for their efforts to thoroughly assess our manuscript. In the following we address your and each reviewer's concerns point-by-point.
We hope that we could adequately address all the issues raised.
In this revision, we have also updated the figures, they are now created with Inkscape rather than RStudio, which gives a more elegant result.
The content of the figures did not change.

@@

Regarding the covariation of DTH, DTL, and DRF, please see our response to your comment about pages 15-16 below.

@@

We do not assume that NFC completely accounts for their covariation.
We have computed an exploratory model which includes the covariation of the three factors as you suggested in the comment below, and it was not superior to the confirmatory model regarding fit measures (please see our response to your comment about pages 15-16).

@@

The *lavaan*-function *fitMeasures()* calls the function *lav_fit_measures()*, which uses the robust RMSEA formula by Broseau-Liard, Savalei, and Li(2012, doi: 10.1080/00273171.2012.715252, equation 8).
It corrects for nonnormality of the data, which might be the reason why RMSEA=SQRT((chisq-df)/(df(n-1))) gives a slightly different result.

@@

Thank you for this suggestion.
The three-part-structure was exactly what we intended with this manuscript; a replication in a different sample, an analysis based on our own previous research, and an exploratory analysis to serve as a starting point for future research.
Each part is relevant but not "long enough" to warrant its own paper.
(As we have provided an answer to this issue in our response to your first comment, we would kindly refer to it here.)
